\documentclass[9pt,twocolumn,twoside]{../../styles/osajnl}
\usepackage{fancyvrb}
\journal{i524} 

\title{Machine Learning for Customer churn prediction using big data analytics}

\author[1,*]{Yatin Sharma}

\affil[1]{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}


\affil[*]{Corresponding authors: yatins@indiana.edu}

\dates{project-001, \today}

\ociscodes{Prediction, Bigdata, Apache Spark, MLlib, Hadoop, Analytics}

% replace this with your url in github/gitlab
\doi{\url{https://github.com/cloudmesh/sp17-i524/tree/master/project/S17-IR-2034/report/report.pdf}}


\begin{abstract}
	This project involves use of machine learning algorithms to identify customers
	who are most likely to discontinue using the service or product.
		\newline
\end{abstract}

\setboolean{displaycopyright}{true}

\begin{document}

\flushbottom % Makes all text pages the same height

\maketitle % Print the title and abstract box

\tableofcontents % Print the contents section
\maketitle

\section{Introduction}
	We will use Apache Spark\cite{www-apache-spark} machine learning library for fitting a predictive model on a
	massive dataset. Detailed analysis and modeling will be carried out in Python
	Programming language.

\section{Execution Summary}
The tentative schedule for  this project has been outlined below:
\begin{enumerate}
	\item {March 13-March 19, 2017:} Create virtual machines on Chameleon, FutureSystems
	and Jetstream clouds
	\item {March 13-March 19, 2017:} Deploy Hadoop cluster to the clouds and install the
	required software packages to the clusters and also finalize data.
	\item {March 20-March 26, 2017:} Data Preprocessing and applying transformation to
	extract features from the data.
	\item {March 27-April 09, 2017:} Use MLlib to train and evaluate various machine
	learning algorithms and choose best based on various performance metrics.
	\item {April 10 - April 16, 2017:} Create deployable software packages in Python.
	\item {April 17-April 23, 2017:} Complete Project Report.
\end{enumerate}

\section{Workflow}
The project will make use of the following four components. 
\begin{enumerate}
    \item Apache Spark
    \item Hadoop
    \item Spark MLlib

\end{enumerate}

\section{Deployment}
	We will deploy our application using Ansible\cite{www-ansible} playbook. Deployment
	of Master/slave nodes will be done hadoop/spark distributed cluster environment.
	Different cloud systems that will be used in the project include
	Chameleon,FutureSystems and JetStream.

\section{Benchmarking}
	Performance of the Hadoop/Spark clusters deployed on different clouds will
	compared for benchmarking.

\section{Conclusion}

TBD

\section{Acknowledgement}
TBD

\bibliography{references}
\end{document}
