\subsection{Word2Vec app - key insights}
We trained the Word2Vec model with the wikipedia data of Indian Cricket team
members. We used \textit{List of India ODI cricketers} as seedlist and
downloaded 500 pages from Wikipedia. With this dataset, we observed that the
\textit{synonym} or correlated words were pretty accurate. Some interesting
examples and its explanation:

\textit{sachin -> tendulkar}

\textit{world -> cup}

Sachin Tendulkar \cite{www-wiki-sachin-tendulkar} is famous Indian cricket
player. Naturally, the words \textit{sachin} and \textit{tendulkar} are
highly correlated. The Word2Vec model was able to find this correlation.

Cricket World Cup \cite{www-wiki-world-cup} is one of the most viewed
sporting event and considered as the flagship event of the international
cricket. Hence the words \textit{world} and \textit{cup} are highly correlated
 in the context of cricket. The Word2Vec model was able to find this correlation.

However, when we tried to find the people relationships using the wikipedia
dataset, we could not get good accuracy. For example, \textit{Anjali Tendulkar}
 is wife of \textit{Sachin Tendulkar} while \textit{Dona Ganguly} is wife of
 \textit{Sourav Ganguly} who is another famous Indian Cricket player
 \cite{www-wiki-sourav}. When we provided the test record of

 \textit{sachin,anjali,sourav}

 we did not get good results.

 After observing the wikipedia data, we concluded that there is lot of
 literature  in wikipedia about the cricketers. However, there were very few
 mentions of their family members, coaches, schools etc. Due to this, we were
  not getting good results on the people relationships.

  To augment the Wikipedia data, we decided to crawl news data which provide
 large amount of articles containing people and their relationships. We
 implemented the news crawler as explained in the section
 \ref{newscrawlersection}. After downloading about 200 news articles of 20
 cricketers, our relationships discovery improved a lot. Some interesting
 examples are given below:
 \textit{sachin,anjali,sourav,dona}

 \textit{sachin,anjali,dhoni,sakshi}

 \textit{sachin,cricket,amitabh,hero}

 In first two examples, the Word2Vec model was able to identify the
 people-people relationships, while in third example, the Word2Vec model was
 able to identify the people-profession relationships.







