\documentclass[9pt,twocolumn,twoside]{styles/osajnl}
\usepackage{fancyvrb}
\usepackage[colorinlistoftodos,prependcaption,textsize=normal]{todonotes}
\newcommand{\TODO}[2][]{\todo[color=red!10,inline,#1]{#2}}
\newcommand{\GE}{\TODO{Grammar}}
\newcommand{\SE}{\TODO{Spelling}}
\newcommand{\TE}{\TODO{Term}}
\newcommand{\CE}{\TODO{Citation}}
\journal{i524} 

\title{Docker(Machine,Swarm)}

\author[1]{Shree Govind Mishra}

\affil[1]{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}

\affil[*]{Corresponding authors:shremish@indiana.edu and govindmisharaalld@gmail.com}
\dates{project-000, \today}

\ociscodes{Cloud, I524, Big Data, Virtualisation, Docker, Docker Swarm, Docker Machine , Virtual Machines, VMs, Containers,LInux Containers, lightweight containers,LXC}

% replace this with your url in github/gitlab
\doi{\url{https://github.com/argetlam115/sp17-i524/blob/master/paper1/S17-IR-2021/report.pdf}}

\begin{abstract}
  Docker is a container based technology which helps in the packaging
  and shipping of applications quickly and across networks. Docker is
  being well accepted and appreciated in the Agile Software
  Development workforce and among the DevOps because of their
  attributes of Continous Integeration and testing.To create a cluster
  of Docker Engines into a single docker virtual engine is used
  Docker-Swarm sed which is tested for more than 50,000
  containers. 
\end{abstract}

\setboolean{displaycopyright}{true}

\begin{document}

\maketitle

\TODO{This review document is provided for you to achieve your
  best. We have listed a number of obvious opportunities for
  improvement. When improving it, please keep this copy untouched and
  instead focus on improving report.tex. The review does not include
  all possible improvement suggestions and for each comment you may
  want to check if it applies elsewhere in the document.}

\TODO{Abstract: "being well accepted" is a subjective statement;
  either remove or provide evidence; no evidence for this in the
  paper}

\TODO{You need to make several revisions to the language, spelling
  (please use a spell-checker) and the way you use citations. In
  addition, you need to provide more evidence for some of the claims
  you make in the paper. Refer to the comments below. That being said,
  your paper approaches the task at the right level of detail and is
  helpful in learning about Docker, so well done for that.}

\TODO{Assessment: Some revisions suggested. Please address the review
  comments by end of March.}

\section{Introduction}
\cite{www-docker-2}Docker is an open-source container based
technology. \CE \TODO{When you cite, the citations needs to go at the
  end of the sentences that uses the information.} It is an extension
of Linux Containers (LXC): \GE which is a unique kind of lightweight,
application-centric virtualization that drastically
\TODO{"drastically" is subjective unless it's backed up by a
  reference} reduces overhead and makes it easier to deploy software
on servers. A container allows a developer to package up an
application and all its part includig it's code, \GE \TODO{Please, be
  careful with "it's" versus "its"} stack it runs on, dependencies it
is associated with,system tools and everything the application requirs \SE
to run within an isolated enviorment. This makes it easier for
programmers and developers to run more apps on the same server and it
even makes it easier to package and ship the apps very frequently.
Docker has been able to popularize the container approach in part
because it’s improved the security and simplicity of container
environments. Plus, interoperability is enhanced by its association
with major companies – such as Google, Canonical, and Red Hat – on its
open source element libcontainer.

\section{How Docker differs from VMs}

The virtualisation of application can be obtained with Hyervisors or
Virtual Machine Manager(VMM) which makes it easy for applications to
the run \GE in isolation with one another while sharing the same
underlying hardware articture. VM hypervisors, such as Hyper-V, KVM,
and Xen, all are "based on emulating virtual hardware" \TODO{This
  doesn't need to be a quote. If you are quoting, you need to provide
  the reference from which the quote was taken.} which means they’re
fat in terms of system requirements. \TODO{"fat in terms of system
  requirements" is a colloquialism; please use a different phrase.}
Instead of virtualizing hardware, containers rest on top of a single
Linux instance.A full virtualized system gets its own set of resources
allocated to it, and does a very minimal sharing of thoses
resources. So, \TODO{"So" is too colloquial to use in a paper.} the
developer gets more isolation but each Instance of the VM aslo has
many "Junk VM files" \TODO{Where is this quote coming from?}, which is
not useful to the developers as it gets "heavy".Since they only
require to keep the virtal machine image and it can be kept
small.Thus, the smaller the image is the less we need to store and the
less you need to send around the network which makes them fairly
\TODO{"fairly" is colloquial and not very descriptive; please avoid}
lightwight in comparison to the Virtal Machines. Thus, we can run even
use 1000s of containers on a same host OS. \GE
\cite{www-stackoverflow-docker} \CE A full virtualized system usually
takes time to start whereas the Docker contaier \SE do \GE take even
less than seconds to up start and running with a lower overhead than
the VMs.  Containers are potentially much more efficient than VMs
because they’re able to share a single kernel and share application
libraries.  This can lead to substantially smaller RAM footprints even
when compared to virtualisation systems that can make use of RAM
overcommitment.  Storage footprints can also be reduced where deployed
containers share underlying image layers. IBM’s Boden Russel has done
\TODO{This is unfinished.}


\section{Uses Of Docker}

\subsection{Docker for DevOps}
Another major use of Docker is it's \GE use in the DevOps
community. \TODO{Clarify what DevOps is.} Docker is not there to
replace other configuration management tools and instead can be
incoprporated with other configuration management tools like Chef,
Puppet, Salt or ansible. The other major benifit of using Docker,
Dockerfiles, the registry amd \SE the whole Docker ecosystem is that
the teams don't have to learn domain specific language as these are
easier to learn than the domain specific Ecosystems \TODO{What are
  Ecosystems? You haven't introduced them so far.}. Though many a
times Docker can be made to work with the other configuration
management tools.\cite{www-docker-1}Docker \CE can also the eliminate
the need for a development team to have the same versions of
everything installed on their local machine. The repeatable nature of
Docker images makes it easier for them to standardize their production
code and configurations.  Their work has led to the creation of Helios
\TODO{You need to be more specific here. Whose work led to Helios?},
an application that manages Docker deployments across multiple servers
and that alerts them when a server isn't running the correct version
of a container.

\subsection{Docker as Virtualized Sandbox}
\cite{www-docker-1} Docker \CE allows sytems administrators and developers
to build applications that can berun \SE on any Linux distribution or
hardware in a virtualized sandbox without making custom builds for all
the different enviorments.Finally, it’s easy to deploy Docker
containers in a cloud scenario. You can easily integrate it with
typical DevOps environments seamlessly (Ansible, Puppet, etc.) or use
it as a standalone. \GE

\subsection{Docker for continuous integration}
Docker can be used as git for continious integeration \SE. Docker is
similar as changes in the system can be tracked just like chaneges \SE in
the git.  These collaboration features (docker push and docker pull)
are one of the most disruptive parts of Docker. The fact that any
Docker image can run on any machine running Docker is very much
appreciated. But The Docker pull/push are the too new fot \SE the first
time developers and ops guys have ever been able to easily collaborate
quickly on building infrastructure together.\cite{www-docker-2}The \CE app
guys can share app containers with ops guys and the ops guys can share
MySQL and PosgreSQL and Redis servers with app guys.

\TODO{This paragraph needs major revision. First, it's very colloquial
  ("guys", "much appreciated", etc. Second, the meaning is not very
  clear. Git is not a CI tool so the first sentence doesn't make
  sense. It's also hard to understand what features of Git, Docker
  duplicates. Finally, is the Git-like functionality being "too new
  for the first time developers" your subjective assessment, or is
  there any reference you can provide?}

\section{Docker MACHINE}

\cite{www-docker-machine}Docker Machine is a tool that lets you install 
Docker Engine on virtual hosts, and manage the hosts with docker-machine 
commands. You can use Machine to create Docker hosts on your local Mac 
or Windows box, on your company network, in your data center, or on 
cloud providers like AWS or Digital Ocean. Docker Machine is the only 
way to run Docker Engine on Mac or Windows previous to Dockerv1.12 
and starting with the Dockerv1.12 we have Docker for Mac and Docker for 
Windows. Thus we can create a cluster of Docker hosts which is called
a Swarm using Docker Machine.

\TODO{A little too colloquial. For example, instead of "You can use
  Machine to create Docker hosts on your local Mac or Windows box...",
  you can reword "Machine can be used to create Docker hosts on Mac
  and Windows machines, ..." Your style is conversational which is not
  a terrible thing, but you need to make it a little less so for a
  paper like this.}

\section{Docker SWARM}

\cite{www-docker-swarm}Docker Swarm \CE provides native clustering
capabilites to turn a group of Docker engines into a single, vrtual \SE
Docker Engine. These help you scale up the applications as if these
all are running on a single,huge \TE computer.It does so by providing
a stabdard \SE Docker API where if any tool which communicates with
the Docker deamon can use Docker Swarm to transparently scale to
multiple hosts: Dokku, Docker Compose, Krane, Flynn, Deis, DockerUI,
Shipyard, Drone, Jenkins and, of course \TE, the Docker client itself.
Docker Networking, Volumes and plugins can also be used through their
respective Docker commands via Swarm. Swarm has been tested and is
production ready to scale up to one thousand (1,000) nodes and fifty
thousand (50,000) containers with no performance degradation in
spinning up incremental containers onto the node cluste \TODO{This is
  a very specific quantitative statement that needs a citation; also,
  spelling/punctuation} Swarm also comes with a built-in scheduler,
but you can easily plugin the Mesos or Kubernetes backend while still
using the Docker client for a consistent developer experience. To find
nodes in your cluster, Docker Swarm can use either a hosted discovery
service, static file, etcd, consul and zookeeper depending on what is
best suited for your environment.


\section{Ecosystem Support to Docker}

\cite{www-docker-1}Finally \CE, it’s easy to deploy Docker containers
in a cloud scenario. You can easily integrate it with typical DevOps
environments seamlessly (Ansible, Puppet, etc.) or use it as a
standalone. The main reason it’s so popular \TODO{How popular is it?
  You need to provide evidence.} is simplification, says Ben Lloyd
Pearson via opensource.com. \TODO{Who is Ben Lloyd and why would we
  want to listen to him? You shouldn't cite specific people by name,
  but their work; the work should speak for itself.} You can do local
development within a system that is identical to a live server; deploy
various development environments from your host that each use their
own software, OS, and settings; easily run tests on various servers;
and create an identical set of configurations, so that collaborative
work isn’t ever hindered by parameters of the local host.Ecosystem
support for Docker is improving with every passing day
\TODO{subjective, please avoid} as it is gaing \SE the popularity
among the developers and the system operators.

Operating Systems suppport to Docker: Is compatible with virtually
any distribution with a 2.6.32 + kernel RedHat Docker collaboration to
work with across fedora and other(2.6.32)+.

It is compatible with Private PaaS(Platform as a Service) technolgies:
OPen Shift, Solum(Rackspace and OPenstack).

Public PaaS technologies like Voxoz, Cocaine(Yandex),Biadu,etc.

Ecosystem Support for IaaS is present via Rackspace,Digital Ocean,
AWS(Amazon Web Services), AMI,etc.

Orchestration tools Support and Integeration with:
Chef,Puppt,Jerkins,Travis,Ansible..

In Open Stack Docker integeration into NOVA(compatibility with
Glance,Horizon)are aslo present

\section{Shortfalls of Docker}

Though dockers are leagcy virtualization techniques, they are not a go
to \SE solution for all kinds of virtualization and cannot be considered
as a replacement of the VMs.

VMs are self constarined \SE with as they have a unique operating
system(OS), drivers and application components whereas the containers
are dependent as containers under Docker cannot run on Windows server.

VMs provide high level of isolation as the system's underlying
hardware resources are all virtualized and thus any bugs or viruses
could not affetc the other VM in the virtualized enviorment \SE.

The kinds of tools and technologies required to manage the containers
are still lacking in the industry and thus only a few management tools
from companies like Google and Docker like Kubernetes and SWarm
respectively are present which is not a good situation for an
open-source products

\section{Future with Docker}

Docker Inc has set a clear path on the development of core
capabilities (libcontainer), cross service management (libswarm) and
messaging between containers (libchan). Docker's key open source
project is libcontainers ,which is on it's \GE way to becomiing \SE
the default standard for Linux-based technology.  Libcontainers
enables the containers to work with the Linux namespace, control
groups, capabilities, AppArmor security profiles, network interfaces
and firewalling rules in a consistent and predictable way .
\cite{www-docker-1}Libcontainers \CE is getting help from Google,
RedHat, and Parallels to build the program asthey will work with
docker as core maintainers of the code.  libconatiner which is written
natively in Google's Go, is also being ported into other
languages. Microsoft may be porting it to ASP.NET.  Parallels' libct,
which includes libcontainer's functionality, has native C/C++ and
Python bindings. Microsoft is even jumping on board \TODO{too
  colloquial} by bringing Docker to their Azure platform, a
development that could potentially make integration of Linux
applications with Microsoft products easier than ever before.



\section{Conclusion}

\cite{www-docker-3}With \CE more than 1200 Docker Contributors ,
10,000 Dockerized Applications at index.docker.io 3 to 4 million
Developers using Docker, 300 Million Downloads, 32,0000 Docker related
Projects and 70 percent of enterprise using DockerIt \TODO{You need to
  provide a source for quantitative claims like this} is not an
exaggeration \TODO{"is not an exaggeration" is too colloquial} that
with Docker Ecosystem there is a greater potential for some advanced
deployment tools that combine containers, configuration management,
continuous integration, continuous delivery and service orchestration
in the days ahead.


\bibliography{references}

\end{document}

