\documentclass[9pt,twocolumn,twoside]{../../styles/osajnl}
\usepackage{fancyvrb}
\journal{i524} 

\title{Deploying CouchDB Cluster}

\author[1,*,+]{Ribka Rufael}


\affil[1]{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}

\affil[*]{Corresponding authors: rrufael@umail.iu.edu}
\affil[+]{HID: S17-IO-3016}

\dates{Project: S17-IO-3016, \today}

\ociscodes{CouchDB}

% replace this with your url in github/gitlab
\doi{Report: \url{https://github.com/rrufael/sp17-i524/blob/master/project/S17-IO-3016/report/report.pdf}\\
Code: \url{https://github.com/rrufael/sp17-i524/tree/master/project/S17-IO-3016/code}}



\begin{abstract}
  This project focuses on deployment of CouchDB Cluster using Ansible
  playbook on Ubuntu Chameleon Cloud VMs and benchmarking of the
  deployment. \newline
\end{abstract} 

\setboolean{displaycopyright}{true}

\begin{document}

\maketitle

\section{Introduction}

CouchDB \cite{www-Couchdb} is a no sql database management system
under Apache. Data is stored as documents in CouchDB. In this project
CouchDB cluster of one or more Chameleon cloud VMs is deployed using
Ansible playbook and benchmarking is done to measure the time it took
for deployement using Bash scripts.After installation of CouchDB
cluster on Chameleon cloud VM, benchmarking test will be performed on
measuring write and read time on CouchDB database. The dataset which
is going to be used for write and read on CouchDB is the wine review
dataset \cite{www-WineReview}.

\section{Execution Plan}

This section depicts week by week execution plan for the project. My
plan is to finish the project in six weeks. To accomplish this I need
Chameleon cloud allocation for six weeks. I plan on using 10 node
hours per week. The anticipated node hours I will need to complete
the project is 60 node hours on Chameleon cloud.

\subsection{Week 1}

I was able to develop an initial Ansible script that will deploy
CouchDB on Ubuntu 16.04 VM , upon successul installation the script
will start CouchDB and then it will stop CouchDB on the remote VM. I
booted Chameleon VM using Cloudmesh and then run Ansible playbook from
my local machine. The tasks in my playbook run successfully.

\subsection{Week 2}

Run Ansible playbook to deploy CouchDB on Chameleon Cloud
VM. Benchmark time it takes to deploy CouchDB on Chameleon Cloud VM

\subsection{Week 3}

Extend the Ansible script developed in Week 1 to deploy CouchDB into
two Chameleon Cloud VMs.

\subsection{Week 4}

Run Ansible playbook to deploy CouchDB on two Chameleon Cloud
VMs. Benchmark time it takes to deploy CouchDB on Chameleon Cloud VMs.

\subsection{Week 5}

Analysis of the benchmark results for deployment of CouchDB
cluster. Document results in report and finalize report.

\subsection{Week 6}

Load the wine review dataset into CouchDB database, benchmark write time
and read time.

\section{Technologies Used}
\begin{itemize}
\item[$\bullet$] Ansible
\item[$\bullet$] Cloudmesh
\item[$\bullet$] Other technologies TBD
\end{itemize}

\section{Deployment}
TBD

\section{Benchmark Results}
TBD

\section{Conclusion}
TBD
\section*{Acknowledgements}

TBD



% Bibliography

\bibliography{references}
 



\end{document}
